\input{../HeadMatter.tex}
	

\part*{Assignment 3 (35\%)- Project Management Initiating and Planning Documents}


\begin{tabularx}{\textwidth}{ |X|X| }
	\hline
	\textbf{Issue Date:} & 16$^{th}$ March 2021\\
	\hline 
	\textbf{Submission Date:}  & 26$^{th}$ April 2021\\
	\hline
\end{tabularx}

\section*{Introduction}

In this assignment you are required to create a detailed project plan for a project of your choice.  The project plan should include the traditional project management documents as well as a post contract award BIM execution plan.  You are free to use the documentation pack used for Assignment 2.\\

\begin{enumerate}
	\item Document Management 
	\item Project Management
	\item Model Coordination
	\item Field Management
	\item Data Analytics
\end{enumerate}

You have been added to a BIM360 project entitled 'PM \& BIM Assignment 2 - 2020-2021'.  A screenshot of a portion of the model is shown in figure \ref{fig:thumbnail}.  BIM360 can be accessed at this link - \href{https://docs.b360.autodesk.com/}{docs.b360.autodesk.com/text}


\section*{Scenario}

Select a project with which you are familiar. The project can be work, social or sports based.  The project must have at least 20 tasks and a maximum of 30.\\

Develop the following items as detailed below. Descriptions of items 1 to 10 are available in the PMI’s Guide to the PMBOK®, 5th Edition and in the lecture notes.\\

The objective of this assignment is to produce a comprehensive project plan. Your project management plan should not contain any project management theory. The text of the document should clearly show how the various aspects of the project are going to be managed. You are encouraged to use standard templates and methodologies.\\

Your final document should be of professional standard in terms of content, layout and completeness. In essence, the completed document should be suitable for presentation to a prospective client.\\

The Reflective Statement should detail your learning experience while undertaking this coursework and your opinion on its relevance to the subject, etc.\\

You are encouraged to use Microsoft Project for as many of the deliverables as possible.\\

This is a practical assignment. Your project management document should fully based on the practical implementation of project management theory.\\


\begin{table}[ht]
	\centering
	\begin{tabular}{|c|l|c|c|}
		\hline
		\textbf{Item} & \textbf{Description} & \textbf{Maximum Required} & \textbf{Marks \%} \\
		\hline
		\hline

		1  & Project Scope Statement &  2 pages  & 10\% \\
		\hline

		2  & Work Breakdown Structure &  30 elements  & 10\% \\
		\hline

		3  & Resource Breakdown Structure &  15 elements  & 10\% \\
		\hline

		4  & RACI Responsibility Assignment Matrix &  A3 Diagram  & 5\% \\
		\hline

		5  & Network Diagram and Gantt Charts &  A3 Diagrams  & 5\% \\
		\hline

		6  & Risk Management Plan & 4 pages  & 15\% \\
   			&	- Methodology  & & \\
   			&	- Timing of Risk Events  & & \\
   			&	- Risk Register  & & \\
		\hline
		
		7  & Cost Control Plan &  2 pages  & 10\% \\
   			&	- Total value of contract  & & \\
   			&	- Proportion to contractor  & & \\
   			&	- Proportion subcontracted   & & \\
   			&	- Methodology  & & \\
   			&	- Project Cash Flow Profile  & & \\
		\hline

		8  & Communications Plan &  2 pages  & 10\% \\
   			&	- Stakeholder Identification Method  & & \\
   			&	- Information Distribution Plan  & & \\
   			&	- Performance Report Requirements  & & \\
		\hline

		9  & Human Resource Plan &  1 page  & 10\% \\
   			&	- Project Team Acquisition  & & \\
   			&	- Release Criteria  & & \\
		\hline

		10  & Procurement Management Plan &  1 page  & 10\% \\
   			&	- Seller Selection Procedure  & & \\
   			&	- Contract Types  & & \\
		\hline

		11  & Reflective Statement &  1 page  & 5\% \\
		\hline
		\hline
        & & \textbf{Total} & \textbf{100\%} \\
		\hline
	
	\end{tabular}
	\caption{Table }
	\label{tab:AM}
\end{table}


\newpage
\section*{Report}
A single report of 4000 words should be submitted by each team.  Your report should be laid out in a professional manner, as would be done for a client or employer.  This involves, \emph{inter-alia}, a cover page, table of contents, and logical sectioning.  You report must include, but is not limited to:
\begin{itemize}
	\item Details of the methodology used to create each component
	\item Screen captures and images of system functionality
	\item Details of any challenges that you experienced with the application
	\item Commentary on learning experience and the skills you developed during the production of this assignment.
\end{itemize}
  


\section*{Late Submission}
Failure to submit your assignment on or before the date and time indicated on Moodle will result in a penalty of 5\% per day or part thereof.


\end{document}