\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 4 (15\%) - Kiosk Project}\\
\end{flushleft}


\textbf{Introduction}\\
This project expands the briefs provided in Design Studio 2 for the Kiosk Project.\\

\textbf{General Arrangement Drawings - Services Layouts }\\
Create Plans, Elevations and Sections necessary to communicate design intent for the following systems and arrangements:

\begin{enumerate}
	\item Lighting System
	\item Power System, incl. Equipment
	\item Communications and Data System, incl, Equipment
	\item Potable (Hot and Cold) Water System.
	\item Waste-water System
\end{enumerate}

In addition to the items listed above, you are required to indicate how your kiosk will interface to the general services of LIT.  This should take the form of general arrangement drawings for:
\begin{enumerate}
	\item Connection of Power to LIT system
	\item Connection of Potable Water to LIT system
	\item Connection of Waste-water to LIT System
	\item Connection of Communications \& Data to LIT System
\end{enumerate}

Your connection drawings should take into consideration the location of existing services, and issues that may present in hiding these service connections.\\

\textbf{Particular Specification}\\
You are required to create specifications for the items listed below:
\begin{enumerate}
	\item Lighting System
	\item Power System, incl. Equipment
	\item Communications and Data System, incl, Equipment
	\item Potable (Hot and Cold) Water System.
	\item Waste-water System
\end{enumerate}

Your specifications should provide detail of the material types and sizes.  Your equipment and fixtures specification should provide generic descriptors of your chosen items where necessary.  Where specific makes and models are required, these are to be specified. \\

Your final specification \textbf{must not exceed 6 pages}, including title page and section headings.\\

\textbf{Design Report}\\
You are required to submit a Design Report highlighting the key features and benefits of your design, and the areas where improvement or change may be necessary.  This report should be written in a professional manner, contain logical sectioning, etc. as would be done for a client.\\  Your report \textbf{must not exceed 1000 words}, excluding headings and title information.\\


\textbf{Submission}\\
You are required to submit a single zip folder of all drawings and specifications.  The zip folder should contain logical sub-folders as necessary.  All drawings are to be submitted as .pdf files.  All specification and report documents are to be submitted as .pdf files.  Please note that hand drawings and/or hand written reports will not be accepted.\\

Upon completion your zip file is to be uploaded to Moodle on or before the date and time specified.  The submission date and time will coincide with the submission of the studio project.\\  

\textbf{Late Submission}\\
Failure to submit your assignment on or before the date and time indicated on Moodle will result in a penalty of 5\% per day or part thereof.  

\vspace{0.5cm}
\textbf{Marking Scheme}\\

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{p{8cm}  p{2cm} }
     \toprule
      \textbf\large{Element} & \textbf\large{Proportion} \\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      \textbf{General Arrangement Drawings (Kiosk)} & \textbf{30\%}\\
      \textbf{Service Connection Drawings} & \textbf{25\%}\\
      \textbf{Particular Specification} & \textbf{30\%}\\      
      \textbf{Design Report} & \textbf{15\%}\\     
      \\ \bottomrule
      \end{tabular}
      \label{tbl:markSchemeAsmt4}
      \end{center}
 \end{table}

\newpage

\textbf{Sample Specification}\\

...\\
Data outlets shall be wired with CAT 6 cables.\\
...\\
Wiring shall be carried out in 2.5 mm PVC insulated copper cabling\\
...\\

\end{document}