\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 2 (40\%)- Project Scope Statement}\\
\end{flushleft}

In this assignment you will create a Scope Statement for a project of your choosing.  You do not need to choose a constrction related project, however the scope statement must cover the key topics identified and discussed in lectures.  Your chosen project will require approval from me before you start.  The key deliverables for this project are:

\begin{enumerate}
	\item Email proposal, maximum of 100 words, outlining your chosen project
	\item Detailed Scope Statement for your project, subject to an overall maximum of 1500 words.
\end{enumerate}


\textbf{Suggested Approach}

\begin{itemize}
	\item Choose a project from a domain that you are comfortable working within.  
	\item Refer to the lecture notes, and identity the key headings necessrary for a comprehensive Scope Statement
	\item Keep your writing clear and concise.  Avoid the typical over-explanation common in academic writing.
	\item A Scope Statement is a live document.  Ensure your document layout is clear and allows for easy access to key sections. 

\end{itemize}


\textbf{Submission}\\
Your completed assignment comprising all computer files are to be zipped into a single file and uploaded to Moodle on or before the date and time indicated.  Key components of the submission are:
\begin{itemize}
	\item Acrobat file (.pdf)
	\item Word file (.docx)
\end{itemize}



\textbf{Marking Scheme}

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{p{9cm}  p{3cm} }
     \toprule
      \textbf\large{Element} & \textbf\large{Proportion} \\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      \textbf{Document Layout} & \textbf{10\%}\\
      \textbf{Scope Statement Detail} & \textbf{70\%}\\
      \textbf{Clarity of language} & \textbf{20\%}\\
      \\ \bottomrule
      \end{tabular}
      \label{tbl:markSchemeAsmt3}
      \end{center}
 \end{table}

\end{document}