\input{HeadMatter.tex}
%     _            _                                  _     ____  
%    / \   ___ ___(_) __ _ _ __  _ __ ___   ___ _ __ | |_  |___ \ 
%   / _ \ / __/ __| |/ _` | '_ \| '_ ` _ \ / _ \ '_ \| __|   __) |
%  / ___ \\__ \__ \ | (_| | | | | | | | | |  __/ | | | |_   / __/ 
% /_/   \_\___/___/_|\__, |_| |_|_| |_| |_|\___|_| |_|\__| |_____|
%                    |___/                                        

\begin{flushleft}
\Large\textbf{Practical 2 - MS Project Resources}\\
\end{flushleft}



In this assignment you will take an existing skeletal project plan, add resources and develop a preliminary cost model that will be copied to excel for further analysis.
\begin{enumerate}
	\item Populate the Resource Sheet with the data below.  You can assume that overtime and cost-per-use will not apply, and that all accruals will be 'Prorated'
	\item Apply the resources to the Gantt chart appropriately. Note that Managerial and supervisory staff will not be applied to any task at 100\% 
	\item Allow overallocation of resources to occur. As part of this exercise, we are going to examine the strategies that can be implemented to correct over-allocation.  
	\item Save a baseline view of your plan
	\item Undertake a controlled leveling of resources.
	\item Examine the 'Task Usage' sheet and copy the cost data to excel in order to create a cost profile for the project.
\end{enumerate}


\begin{table}[h]
	\centering
		\begin{tabular}{| l | r |} \hline
			\textbf{Resource}	& \textbf{Rate} \\
			\hline
			Project Manager				&	€120.00/hr	\\
			Construction Manager	&	€100.00/hr	\\
			Site Manager					&	€100.00/hr	\\
			Supervisor 1					&	€60.00/hr	\\
			Supervisor 2					&	€60.00/hr	\\
			Staff A								&	€45.00/hr	\\
			Staff B								&	€45.00/hr	\\
			Staff C								&	€45.00/hr	\\
			Staff D								&	€45.00/hr	\\
			Staff E								&	€45.00/hr	\\
			Staff F								&	€45.00/hr	\\
			\hline
		\end{tabular}
	\caption{Resource Data}
	\label{tab:ResourceData}
\end{table}


Upload a single zip file of your completed plan and excel file to Moodle when you are finished.

\end{document}